---
title: "p8105_hw1_ak5098"
output: github_document
date: "2024-09-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)
library(tidyr)


```

```{r}
#PROBLEM 1

install.packages("palmerpenguins")
data("penguins", package = "palmerpenguins")


nrow(penguins)
ncol(penguins)
head(penguins)

mean(pull(penguins, flipper_length_mm), na.rm = TRUE)

penguinplot = ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color=species)) +geom_point()
penguinplot
ggsave("penguinplot.png")


```
#Summary of Penguins
important variable names: species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, year
number of rows: 344
number of columns: 8
mean fipper length in mm: 200.9152

```{r}
#PROBLEM 2

samp=rnorm(10)
logical = samp > 0
char = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J")
factor = sample(c("low", "medium", "high"), size = 10, replace = TRUE)

problem2 = 
  tibble(samp, logical, char, factor)

print(problem2)

mean(pull(problem2, samp))
mean(pull(problem2, logical))
mean(pull(problem2, char))
mean(pull(problem2,factor))
```
The mean can be taken for the numeric and logical vectors. It cannot be taken for the character and factor vectors. 

```{r}
#PROBLEM 2 CONT.
as.numeric(logical)
as.numeric(char)
as.numeric(factor)
```
With logical, every TRUE converts to 1 and every FALSE converts to 0. For character vector, every element turns into NA. The same hapens with the factor vector. 
This makes sense in relation to the output from the mean function, because you cannot take the mean for NA. 